---
title: Mortality of zoea 1 larvae of *Taliepus* *dentatus* reared at different temperatures
subtitle: "Reproducible report"
author: "Lucas Bravo, Milena Cano, Mauricio F. Landaeta, Sergio Navarrete, Simone Baldanzi"
output:
  pdf_document: 
  include:
   keep_tex: yes
---

This document reproduces and supports all data work and statistical
analysis of the larval mortality in the paper: swimming performance and
morphometrics of the kelp-crab *Taliepus dentatus* zoea 1 exposed to
different rearing temperatures.

## 1. Libraries

```{r message=FALSE, warning=FALSE, include=TRUE}
library(cowplot)
library(scales)
library(dplyr)
library(gridExtra)
library(tidyverse)
library(ggsci)
library(Rmisc)
library(survminer)
library(survival)
library(MASS)
```

## 2. Import of data base and definition of factors

```{r message=FALSE, warning=FALSE, include=TRUE}

#database import
Mort<-read.delim("~/Desktop/ECOLAB!/paper tesis/mortalidad/mort.txt")
Mort$bino<-Mort$Vivas/100


#Factor
Mort$Temperature<-as.factor(Mort$Temperatura)


#survival plot by temp by each replicate. 
Grafico_frascos<-ggplot(Mort, aes(x=Dia, y=Vivas,colour=Temperature))+
  geom_point() + theme_classic() +
  ggtitle("survival")+facet_wrap(~Temperature*Frasco)+
  labs(x="day", subtitle =
         "replicates (A-B-C) by temperature", y= "Survival (%)")
Grafico_frascos +
  scale_colour_manual(values =
                        c("blue", "orange", "red"),
                      labels=c("12°C","15°C","17°C"))
```

## 2.1 table with statistics for LT50 and Kaplan-meier Analysis

```{r message=FALSE, warning=FALSE, include=TRUE}
#Estadisticos basicos (SD, SE, CI, MEAN)
LT50_summary<- summarySE(Mort, measurevar="bino",
                         groupvars=c("Temperatura","Dia"))
print(LT50_summary)
```

## 3. GLM analysis and LT50% plot.

```{r message=FALSE, warning=FALSE, include=TRUE}

#separation of the table by temp 
mort_12<-LT50_summary[1:11, ]
mort_15<-LT50_summary[12:22, ]
mort_17<-LT50_summary[23:32,]

#GLM analysis for each temp

model1<-glm(data=mort_12, bino ~ Dia, family=quasibinomial())
summary(model1)

model2<-glm(data=mort_15, bino ~ Dia, family=quasibinomial())
summary(model2)

model3<-glm(data=mort_17, bino ~ Dia, family=quasibinomial())
summary(model3)

#Dose.p function to find moment at which 50% of the population has
#died based in the glm models made above

print(dose.p(model1, p = 0.5))
print(dose.p(model2, p = 0.5))
print(dose.p(model3, p = 0.5))

# LT50% plot with values given by dose.p

lt50<-c(4.531844, 6.493628, 5.919705)
CI<-c(0.6121778*1.95, 0.11405*1.95, 0.2142654*1.95)
temp<-c(12, 15,17)
data_final<-data.frame(lt50, CI, temp)
data_final$temp<-as.factor(data_final$temp)


lt50_plot<-ggplot(data_final, aes(x=temp, y=lt50, fill=temp))+ 
  geom_bar(stat="identity") + theme_classic() + 
  labs(title = "Lethal doses", 
       x="", y="Day", fill= "Temperature") + 
  scale_fill_manual(values =c("blue", "orange", "red"),
                    labels=c("12°C","15°C","17°C")) 
lt50_plot + geom_errorbar(aes(ymin=lt50-CI, ymax=lt50+CI),
                          width=.2, position=position_dodge(0.05)) +
  geom_text(aes(label=c("4.50","6.50","5.90")),position =
              position_dodge(0.9), vjust = 10) 

```

## 3.1 Kaplan-Meier Analysis

```{r message=FALSE, warning=FALSE, include=TRUE}

#Vector for creating correct data table
repV<- Mort$Muertas 
  repV[repV=="0"]<-1

#Datatable KAP for analysis
KAP<-Mort %>%
  mutate(count = repV) %>%
  uncount(count)

# Adding Status column (binary in which 1=no death; 2=death on that day)
KAP$STATUS <- ifelse (KAP$Muertas==0, 1, 2)
survObj <- Surv(time=KAP$Dia, event=KAP$STATUS==2)

#Kaplan-Meier analysis 
sfit <- survfit(Surv(Dia, STATUS)~Temperatura, data=KAP)

#Ploting Kaplan-meier results
ggsurvplot(sfit, conf.int=TRUE, pval=TRUE, risk.table=FALSE, 
           legend.labs=c("12°C", "15°C","17°C"),
           legend.title="Temperature",  
           palette=(c("blue", "orange", "red")), 
           risk.table.height=.15, ylab="Survival (%)", xlab="Day")
```
