---
title: Supplementary data 1
subtitle: "Reproducible report"
author: Lucas Bravo<sup>1</sup>, Milena Cano<sup>1</sup>, Mauricio F. Landaeta<sup>2,3</sup>, Sergio Navarrete<sup>4,5,6</sup>, Simone Baldanzi<sup>1,2</sup>
output: 
 html_document:
   keep_md: yes
---

<sup>1</sup> Laboratorio de Ecofisiología y Ecología Evolutiva Marina
(e°CO2lab), Facultad de Ciencias del mar y de Recursos Naturales,
Universidad de Valparaíso, Viña del Mar, Chile.

<sup>2</sup> Centro de Observación Marino para Estudios de Riesgos del
Ambiente Costero (COSTA-R), Universidad de Valparaíso, Chile

<sup>3</sup> Laboratorio de Ictiología e Interacciones Biofíscas
(LABITI), Facultad de Ciencias, Universidad de Valparaíso, Valparaiso,
Chile

<sup>4</sup> Estación Costera de Investigaciones Marinas (ECIM),
Pontificia Universidad Católica de Chile, Las Cruces, Chile.

<sup>5</sup> Center for Applied Ecology and Sustainability (CAPES),
COPAS COASTAL, Instituto Milenio en Socioecología Costera, SECOS,
Pontificia Universidad Católica de Chile, Santiago, Chile.

<sup>6</sup> Center for Oceanographic Research COPAS Coastal, Universidad de Concepción, Chile 



This document reproduces and supports all data work and statistical
analysis of the larval survival, geometric morphometrics and swimming
activity in the paper **"Assessing the effect of temperature variability
on the swimming performance, survival and morphometrics of zoea larvae
of the kelp crab *Taliepus dentatus*"**.

# Libraries

```{r chunk_opt, include=FALSE}
knitr::opts_chunk$set(dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE)
```

```{r libraries}
#Mortality libraries
library(cowplot)
library(scales)
library(dplyr)
library(gridExtra)
library(tidyverse) 
library(ggsci)
library(Rmisc)
library(survminer)
library(survival)
library(MASS)
library(here)


#Morphometrics Libraries 
library(Morpho)
library(geomorph)
library(shapes)
library(StereoMorph)
library(readr)
library(ggplot2)

#Swimming libraries
library(tidyverse)
library(lme4)
library(plyr)
library(lmerTest)
library(lme4)
library(car)
library(sjPlot)
library(effects)
library(cowplot)
library(emmeans)
library(sjPlot)
library(multcomp)
library(rlist)
```

# Timeseries of environmental temperature

```{r Timeseries_temp}
montemar<-read.table(here("Montemar-minidot", "miniDOT.dat"))

#MAKING DATETIME COLUMN and ADDING COLUMNS GROUPS
montemar_date <- montemar %>%
  unite("date", V1:V3, sep = "-")
montemar_date$date<-anytime::anydate(montemar_date$date)

montemar_date$jd <- yday(montemar_date$date)  
montemar_date$day<-day(montemar_date$date)
montemar_date$month<-month(montemar_date$date)
montemar_date$year<-year(montemar_date$date)

#mean temperature by days
Day_temp<-montemar_date %>%        
  group_by(year,month, day) %>%   
  dplyr::summarize(mean_temp = mean(V6), SD=sd(V6))  
Day_temp<-Day_temp %>% mutate(Date = make_date(year, month, day))
Day_temp<-Day_temp[1:365,] #RUN TO TAKE ONLY FIRST YEAR (2021 JAN-2022 JAN)
Day_temp$month<-as.factor(Day_temp$month)

#mean temperature by month
Month_temp <- montemar_date %>% 
  group_by(year,month) %>%  
  dplyr::summarize(mean_temp = mean(V6, na.rm=T), SD=sd(V6,na.rm=T), n=n())

Month_temp

ggplot(Day_temp, aes(x=Date, y=mean_temp)) + geom_point() + geom_line()+ theme_bw() + scale_x_date(date_labels = "%b", date_breaks = "1 month") + 
  geom_errorbar(aes(ymin=Day_temp$mean_temp-SD, ymax=Day_temp$mean_temp+SD), 
                width=.2, position=position_dodge(0.05),alpha=0.5) +
  labs(y="Temperature (C°)")+ theme(plot.margin = margin(0.2,0.5,0.2,0.2, "cm")) + labs(x=element_blank())
```

# Mortality

## 1. Import of data base and definition of factors

```{r mort_data}
#data are available in the online version of the article, remember to import environment 
Mort <- read.delim(here::here("mortality/mort.txt"))
Mort$bino<-Mort$alive/100

#Temperature as factor
Mort$Temperature<-as.factor(Mort$Temperature)
```

## 2. Data summary

```{r mort_summ}
# SD, SE, CI and  MEAN
LT50_summary<- summarySE(Mort, measurevar="bino",
                         groupvars=c("Temperature","Day"))
head(LT50_summary)
```

## 3. Generalized Lineal Model (GLM) analysis and LT50%

```{r glm_lt50}

#separation of the table by temp 
mort_12<-LT50_summary[1:11, ]
mort_15<-LT50_summary[12:22, ]
mort_17<-LT50_summary[23:32,]

#GLM analysis for 12°C
model1<-glm(data=mort_12, bino ~ Day, family=quasibinomial())
summary(model1)

#GLM analysis for 15°C
model2<-glm(data=mort_15, bino ~ Day, family=quasibinomial())
summary(model2)

#GLM analysis for 17°C
model3<-glm(data=mort_17, bino ~ Day, family=quasibinomial())
summary(model3)

#Dose.p function to find moment at which 50% of the population has died (LT50%) based in the glm models made above

#LT50% for 12°C
dose.p(model1, p = 0.5)

#LT50% for 15°C
dose.p(model2, p = 0.5)

#LT50% for 17°C
dose.p(model3, p = 0.5)

# LT50% values with their CI
lt50<-c(4.531844, 6.493628, 5.919705)
CI<-c(0.6121778*1.95, 0.11405*1.95, 0.2142654*1.95)
temp<-c(12, 15,17)
data_final<-data.frame(temp,lt50, CI)
data_final$temp<-as.factor(data_final$temp)
data_final

```

## 4. Kaplan-Meier Analysis

```{r KAP_MEI}

#Vector for creating correct data table
repV<- Mort$dead 
  repV[repV=="0"]<-1

#Datatable KAP for analysis
KAP<-Mort %>%
  mutate(count = repV) %>%
  uncount(count)

# Adding Status column (binary in which 1=no death; 2=death on that day)
KAP$STATUS <- ifelse (KAP$dead==0, 1, 2)
survObj <- Surv(time=KAP$Day, event=KAP$STATUS==2)

#Kaplan-Meier analysis 
sfit <- survfit(Surv(Day, STATUS)~Temperature, data=KAP)
summary(sfit)
#Ploting Kaplan-meier results
ggsurvplot(sfit, conf.int=TRUE, pval=TRUE, risk.table=FALSE, 
           legend.labs=c("12°C", "15°C","17°C"),
           legend.title="Temperature",  
           palette=(c("blue", "orange", "red")), 
           risk.table.height=.15, ylab="Survival", xlab="Day")

```

*Fig 1. Kaplan-meier survival curve (lines) for each temperature with
their confidence interval (shaded color)*

------------------------------------------------------------------------

# Geometric Morphometrics

##Digitizing

```{r digi_data}
curve.v1<- c("organo_dorsal","esq_izq_caparaza")
curve.v2<- c("punta_espina_dorsal","punta_espina_dorsal")
curve.v3<- c("curvaD_espina_dorsal","curvaI_espina_dorsal")
curve<- matrix(c(curve.v3,curve.v2, curve.v1), ncol = 3)
# take-off "#" of the digitizeimages function in order to visualize each picture digitalization on rmarkdown. 
#digitizeImages(image.file="morphometric larva/ZOEA1_FOTOS/12°C", landmarks.ref="morphometric larva/landmarks.txt", curves.ref = curve, shapes.file ="morphometric larva/zoea1")
#digitizeImages(image.file="morphometric larva/ZOEA1_FOTOS/15°C", landmarks.ref="morphometric larva/landmarks.txt", curves.ref = curve, shapes.file ="morphometric larva/zoea1")
#digitizeImages(image.file="morphometric larva/ZOEA1_FOTOS/17°C", landmarks.ref="morphometric larva/landmarks.txt", curves.ref = curve, shapes.file ="morphometric larva/zoea1")
```

## 1. Import Digitized pictures, grouping files and links for landmarks

```{r geom_data}
#data are available in the online version of the article, remember to import environment 
DIGIDAT<-readShapes(here::here("morphometric/zoea1"))

# Telling R the database is from steremorph
array_data<-readland.shapes(DIGIDAT, nCurvePts= c(7,7))

# Importing traits
traitF<- read_delim("/Users/lucasb/Desktop/ECOLAB!/paper tesis/morphometric larva/trait1.txt", 
                    delim = "\t", escape_double = FALSE, 
                    trim_ws = TRUE)
head(traitF)

# assigning columns as factors
traitF$Temp<- as.factor(traitF$Temp)
traitF$Replica<-as.factor(traitF$Replica)
traitF$Day<-as.factor(traitF$Day)

# importing file linksgeo to create lines connections between landmarks and semilandmarks
linksgeo <- read_delim("/Users/lucasb/Desktop/ECOLAB!/paper tesis/morphometric larva/links.txt", delim = "\t", 
                    escape_double = FALSE, col_names = FALSE, 
                    trim_ws = TRUE)
linksgeo<-as.matrix(linksgeo)
```

## 2. Generalized Procrustes Analysis (GPA)

```{r GPA}
#Generalized Procrustes Analysis
GPA<- gpagen(array_data,ProcD=FALSE, print.progress = FALSE, curves=array_data$curves) 
#procD=false, bending energy is the correct criterion for optimizing the positions of semilandmarks

gdf<- geomorph.data.frame(GPA, Temp=traitF$Temp, replica=traitF$Replica)
```

## 3. Principal Components Analysis (PCA)

```{r PCA}
# Mean shape of all the individuals and adding links and numbers for each landmark and semilandmark
msh <- mshape(GPA$coords)
plot(msh, links = linksgeo)

# plot of all landmarks and semilandmarks digitized in grey and mean shape in black
plotAllSpecimens(GPA$coords, links = linksgeo, plot.param = list(txt.cex = 1.5, txt.col = "#D53E4F", pt.bg = "#BDBDBD", link.col = "black", mean.bg = "black"))

# Principal Components Analysis 
PCA<-gm.prcomp(GPA$coords)
summary(PCA)

# Principal components analysis by replica
AnError<-procD.lm(coords~replica, data = gdf, iter = 999, RRPP = TRUE)

summary(AnError)

(0.0127297/0.0138194)*100

# Error explained by miss-digitazion (%)
(0.0010897/0.0138194)*100 

```

```{r PC1-2_plot}
# Taking out PCA coordinates to create a plot with ggplot
df_out <- as.data.frame(PCA$x)

# ggplot for the PC1 and PC2
PCA1<-ggplot(data=df_out, aes(x=Comp1, y=Comp2, col=
                          gdf$Temp)) + geom_point(size=3, show.legend = FALSE) + theme_light() + labs(x="PC1=34.4%", y="PC2=20.6%") + scale_color_manual(values =c("blue","orange", "red"))
PCA1
```

*Fig 3a. First (PC1) and second (PC2) principal components distribution
with their explained variance (%)*

```{r Shp_plot_pc1-2, eval=FALSE}
# Plots of the mean shape (grey) against mínimum shape (black) of PC1 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp1$min, method =  "points", 
                links = linksgeo)

# Plots of the mean shape (grey) against maximum shape (black) of PC1 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp1$max,method = "points", 
                links = linksgeo)

# Plots of the mean shape (grey) against mínimum shape (black) of PC2 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp2$min, method =  "points", 
                links = linksgeo)

# Plots of the mean shape (grey) against maximum shape (black) of PC2 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp2$max,method = "points", 
                links = linksgeo)
```

```{r PC1-3_plot}
# ggplot for the PC1 and PC3
PCA2<-ggplot(data=df_out, aes(x=Comp1, y=Comp3, col=
      gdf$Temp))+geom_point(size=3) + theme_light() +
  labs(x="PC1=34.4%", y="PC3=14.6%", shape="Day", col="Temperature")+ scale_color_manual(values =c("blue", "orange", "red"))
PCA2
```

*Fig 3b. First (PC1) and second (PC3) principal components distribution
with their explained variance (%)*

```{r Shp_plot_pc1-3, eval=FALSE}
# Plots of the mean shape (grey) against mínimum shape (black) of PC1 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp1$min, method =  "points",
                links = linksgeo)

# Plots of the mean shape (grey) against maximum shape (black) of PC1 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp1$max,method = "points",
                links = linksgeo)

# Plots of the mean shape (grey) against mínimum shape (black) of PC3 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp3$min, method =  "points",
                links = linksgeo)

# Plots of the mean shape (grey) against maximum shape (black) of PC3 (with default magnification=1)
plotRefToTarget(msh, PCA$shapes$shapes.comp3$max,method = "points",
                links = linksgeo)
```

## 4. Canonical Variance Analysis (CVA)

```{r CVA}
# Column to the Database to later use as grouping
traitF$grouppp<-paste(traitF$Temp, traitF$Day)

# Canonical variance analysis using bonferroni p-value adjustment 
cva1<-CVA(GPA$coords, groups = traitF$Temp, p.adjust.method = "bonferroni",rounds = 1000, robust = "classical")

# P-values (euclides) obtained between groups
(cva1[["Dist"]][["probsEuclid"]])

# Procrustes distances (euclides) between groups
(cva1[["Dist"]][["GroupdistEuclid"]])

Cva_out<-as.data.frame(cva1$CVscores)
consensus<-as.data.frame(cva1$groupmeans)
Cva_out$temp<-gdf$Temp

ggplot(data=Cva_out, aes(x=`CV 1`, y=`CV 2`, col=temp)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
labs(x="Canonical variable 1 (76.4%)", y= "Canonical variable 2 (23.6%)", col= "Temperature") + theme_classic() + scale_color_manual(values =c("blue", "orange", "red"), labels=c("12°C","15°C","17°C"))

plotRefToTarget(cva1[["Grandm"]], cva1[["groupmeans"]][,,1], method ="points", links = linksgeo, axes = TRUE, label = FALSE, gridPars = gridPar(tar.pt.bg = "blue", tar.link.col="blue",tar.link.lwd=2, link.col = "grey", pt.bg = "grey", link.lwd = 2, pt.size = 1, tar.pt.size = 1.5))

plotRefToTarget(cva1[["Grandm"]], cva1[["groupmeans"]][,,2], method ="points", links = linksgeo, axes = TRUE, label = FALSE, gridPars = gridPar(tar.pt.bg = "orange", tar.link.col="orange",tar.link.lwd=2, link.col = "grey", pt.bg = "grey", link.lwd = 2, pt.size = 1, tar.pt.size = 1.5))

plotRefToTarget(cva1[["Grandm"]], cva1[["groupmeans"]][,,3], method ="points", links = linksgeo, axes = TRUE, label = FALSE, gridPars = gridPar(tar.pt.bg = "red", tar.link.col="red",tar.link.lwd=2, link.col = "grey", pt.bg = "grey", link.lwd = 2, pt.size = 1, tar.pt.size = 1.5))

```

------------------------------------------------------------------------

# Swimming Performance

## 1. Import database and Tyding

```{r swimm_data}
#data are available in the online version of the article, remember to import environment 
list_of_files <- list.files(path = here::here("swimming R/NEW TRIAL/data"), recursive = TRUE,pattern = "\\.txt$", full.names = TRUE)

#Lapply allows to import all the files in one list
loop_full<-lapply(list_of_files, read.delim2)
names(loop_full)<-list_of_files
loop_full<-lapply(loop_full, function(x) { x["frame"] <- NULL; x })
```

```{r 12_loop}
mean_t1_12<-list()
# for loop to make same functions to all files of 12°C 
for (i in 1:14){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2] #Mean velocity by larvae
mean_t1_12[[i]]<-z1
}
names(mean_t1_12)<-list_of_files[1:14] #rownames

# Tidying columns Temp, aquarium and larva.
mean_t1_12<- list.rbind(mean_t1_12)
mean_t1_12$larva<-c(1,2,2,3,3,3,3,4,4,4,5,5,5,5,1,1,2,2,3,3,3,4,4,4,5,1,2,2,2,4,5,5,5)
mean_t1_12$aquarium<-c("A","A", "A", "A", "A", "A" ,"A", "A", "A", "A", "A", "A", "A", "A", "B", "B", "B", "B","B", "B", "B", "B", "B", "B", "B", "C", "C", "C", "C", "C", "C", "C", "C")
mean_t1_12$temp<-rep(12)
mean_t1_12<-mean_t1_12[, c(6,5,4, 1, 2, 3)]
colnames(mean_t1_12)<-c("Temp","aquarium","Larva","Trajectory","Time","IV")
```

```{r 15_loop}
mean_t1_15<-list()
# for loop to make same functions to all files of 15°C 
for (i in 15:25){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity 
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2] #Mean velocity by larvae
mean_t1_15[[i]]<-z1
}
mean_t1_15<-mean_t1_15[c(15:25)]
names(mean_t1_15)<-list_of_files[15:25] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_15<- list.rbind(mean_t1_15)
mean_t1_15$larva<-c(1,1,1,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,5,5,1,1,1,1,1,2,2,2,2,2,2,2,3,1,2,2,2,2,2,3,3,5,5)
mean_t1_15$aquarium<-c("A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "C", "C", "C","C", "C", "C", "C", "C", "C", "C")
mean_t1_15$temp<-rep(15)
mean_t1_15<-mean_t1_15[, c(6,5,4, 1, 2, 3)]
colnames(mean_t1_15)<-c("Temp","aquarium","Larva","Trajectory","Time","IV")
```

```{r 17_loop}
mean_t1_17<-list()
# for loop to make same functions to all files of 17°C 
for (i in 26:39){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity 
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2] #Mean velocity by larvae
mean_t1_17[[i]]<-z1
}
mean_t1_17<-mean_t1_17[c(26:39)]
names(mean_t1_17)<-list_of_files[26:39] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_17<- list.rbind(mean_t1_17)
mean_t1_17$larva<-c(1,1,1,1,2,2,2,2,3,3,3,4,4,4,5,5,5,2,2,3,3,3,3,3,3,3,3,3,3,4,4,5,5,5,5,1,1,1,1,1,1,1,2,2,2,2,2,2,3,3,3,3,3,4,4,4,5,5,5,5,5,5)
mean_t1_17$aquarium<-c("A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "A", "B","B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "B", "C","C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C", "C","C", "C", "C", "C", "C", "C", "C", "C")
mean_t1_17$temp<-rep(17)
mean_t1_17<-mean_t1_17[, c(6,5,4, 1, 2, 3)]
colnames(mean_t1_17)<-c("Temp","aquarium","Larva","Trajectory","Time","IV")
data<-rbind(mean_t1_12,mean_t1_15,mean_t1_17)
```

```{r swimm_tidy}
#Tidying data
data1<-data%>%group_by(Temp,aquarium,Larva) %>%
  dplyr::summarise(Ist_Vel = mean(IV),
                   Tot_Time= sum(Time), Max_Time=max(Time))%>%rowid_to_column(var='ID')
data1$Temp<-as.factor(data1$Temp)
```

```{r Median_swimm}
#Median of instant velocity by temp
medIV <- ddply(data1, "Temp", summarise, grp.med=median(Ist_Vel), Q1=quantile(Ist_Vel, c(0.25), type = 6),Q3=quantile(Ist_Vel, c(0.75), type = 6), IQR=Q3-Q1)
print(medIV)
#Median of max time swimming by temp
medMax <- ddply(data1, "Temp", summarise, grp.med=median(Max_Time),
Q1=quantile(Max_Time, c(0.25), type = 6),Q3=quantile(Max_Time, c(0.75), type = 6), IQR=Q3-Q1)
print(medMax)
```

## 2. Kernel plots

```{r Kernel_IV}
#Non-parametric Kernel Densities plot for instant velocity (IV)
dplot_IV<-ggplot(data1, aes(Ist_Vel, color=Temp))+
  geom_density(kernel = "gaussian")+
  geom_point(aes(x=5.13, y=0),colour="blue",shape=17, size=6)+
  geom_point(aes(x=1.76, y=0),colour="orange",shape=17, size=6)+
  geom_point(aes(x=1.56, y=0),colour="red",shape=17, size=6)+
  theme_classic()+ 
  labs(colour="Temperature", x="Instant Velocity (mm/s)", y="Kernel density")+ 
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  scale_y_continuous(limits = c(0, NA),expand = expansion(mult = c(0, 0.1))) +
  theme(axis.title = element_text(size = 20),axis.text = element_text(size = 20)) +
  scale_colour_manual(values =c("blue","darkorange", "red"))
dplot_IV
```

*Kernel density plot of instant velocity (IV) with their median
(triangle) by temperature*

```{r Kernel_MT}
#Non-parametric Kernel Densities plot for max time swimming (MT)
dplot_Max<-ggplot(data1, aes(Max_Time, color=Temp))+
  geom_density(kernel="gaussian")+
  geom_point(aes(x=10.25, y=0),color="blue",shape=17, size=6)+
  geom_point(aes(x=18.80, y=0),color="orange",shape=17, size=6)+
  geom_point(aes(x=19.25, y=0),color="red",shape=17, size=6)+
  theme_classic()+
  labs(colour="Temperature", x="Max Time Swimming (sec)", y="Kernel density")+ 
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.1))) +
  scale_y_continuous(limits = c(0, NA),expand = expansion(mult = c(0, 0.1))) +
  theme(axis.title = element_text(size = 20),axis.text = element_text(size = 20)) +
  scale_color_manual(values =c("blue","darkorange", "red"))
dplot_Max
```

*Kernel density plot of max time swimming (MT) with their median
(triangle) by temperature*

## 3. Linear mixed effects model with log transformed data

```{r lm_assmptn}
#Checking for normality
shapiro.test(log(data1$Ist_Vel))
hist(log(data1$Ist_Vel))
shapiro.test(log(data1$Max_Time))
hist(log(data1$Max_Time))

#Checking for heteroscedasticity
leveneTest(log(data1$Ist_Vel), data1$Temp)
leveneTest(log(data1$Max_Time),data1$Temp)

```

```{r swimm_lm}
#Linear mixed effects model with Log transformed data of IV. aquarium is a factor with random effects and larva is nested in aquarium 
modIV<-lmer(log(Ist_Vel)~Temp + (aquarium|Larva), data=data1)
summary(modIV)
anova(modIV)
#model diagnostic
plot(modIV,which = 1)
qqnorm(resid(modIV))
qqline(resid(modIV))


#Linear mixed effects model with Log transformed data of MT aquarium is a factor with random effects and larva is nested in aquarium 
modMax<-lmer(log(Max_Time)~Temp + (aquarium|Larva), data=data1)
summary(modMax)
anova(modMax)
#model diagnostic
plot(modMax,which = 1)
qqnorm(resid(modMax))
qqline(resid(modMax))

```

## 4. Pairwise comparisions and log transformed data plots

```{r swimm_pw}
#pairwise comparison using estimated means of instant velocity by temp
meansIV<-emmeans(modIV, pairwise ~ Temp, adjust="bonferroni")
meansIV

#pairwise comparison using estimated means of max time swimming by temp
meansMax<-emmeans(modMax, pairwise ~ Temp, adjust="bonferroni")
meansMax
```

```{r logIV_plot}
#Boxplot of logaritmic IV data 
p1<-ggplot(data1, aes(x=Temp, y=log(Ist_Vel), fill=Temp))+geom_boxplot()+
  stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") +
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic()+labs(x="Temperature", y="IV")+theme(legend.position="none")+
   scale_fill_manual(values =c("blue","darkorange", "red"))+ 
  scale_y_continuous(breaks =c(1,2,0))+  geom_text(x=1.2,y=2.3,label="a",color="red")+
  geom_text(x=2.2,y=1.3,label="b",color="red")+
  geom_text(x=3.2,y=1.3,label="b",color="red")
p1
```

*Boxplot that represents logarithmic IV distribution of the data by
temperature, letters indicate significant difference.*

```{r logMT_plot}
# Boxplot of logaritmic MT data 
p2<-ggplot(data1, aes(x=Temp, y=log(Max_Time), fill=Temp))+
  geom_boxplot()+ stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") + 
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic() + theme(legend.position="none") +
  labs(x="Temperature", y="MTS")+
   scale_fill_manual(values =c("blue","darkorange", "red"))+
  geom_text(x=1.2,y=3,label="a",color="red")+
  geom_text(x=2.2,y=3.5,label="a",color="red")+
  geom_text(x=3.2,y=3.5,label="a",color="red")
p2

```

*Boxplot that represents logarithmic MT distribution of the data by
temperature, letters indicate significant difference.*

```{r Fig_4}
#kernel density plot with inset boxplot of IV
plot.with.inset.IV <-
  ggdraw() +
  draw_plot(dplot_IV) +
  draw_plot(p1, x = .49, y = 0.65, width = .3, height = .35)
plot.with.inset.IV

```

*Fig 4. Kernel density plot of instant velocity swimming by larvae (IV)
with their median (triangle) by temperature, also with an inside boxplot
that represents the logarithmic IV by temperature.*

```{r Fig_5}
#kernel density plot with inset boxplot of MT
plot.with.inset.Max_Time <-
  ggdraw() +
  draw_plot(dplot_Max) +
  draw_plot(p2, x = .49, y = 0.65, width = .3, height = .35)
plot.with.inset.Max_Time

```

*Fig 5. Kernel density plot of max time swimming by larvae (MTS) with
their median (triangle) by temperature, also with an inside boxplot that
represents the logarithmic MTS by temperature.*
