---
title: "Code/data availability"
subtitle: "Reproducible report"
author: Lucas Bravo<sup>1</sup>, Milena Cano<sup>1</sup>, Mauricio F. Landaeta<sup>2,3</sup>, Sergio Navarrete<sup>4,5,6</sup>, Simone Baldanzi<sup>1,2</sup>
output: 
 html_document:
   keep_md: yes
---

<sup>1</sup> Laboratorio de Ecofisiología y Ecología Evolutiva Marina
(e°CO2lab), Facultad de Ciencias del mar y de Recursos Naturales,
Universidad de Valparaíso, Viña del Mar, Chile.

<sup>2</sup> Centro de Observación Marino para Estudios de Riesgos del
Ambiente Costero (COSTA-R), Universidad de Valparaíso, Chile

<sup>3</sup> Laboratorio de Ictiología e Interacciones Biofíscas
(LABITI), Facultad de Ciencias, Universidad de Valparaíso, Valparaiso,
Chile

<sup>4</sup> Estación Costera de Investigaciones Marinas (ECIM),
Pontificia Universidad Católica de Chile, Las Cruces, Chile.

<sup>5</sup> Center for Applied Ecology and Sustainability (CAPES), and
Instituto Milenio en Socioecología Costera, SECOS, Pontificia
Universidad Católica de Chile, Santiago, Chile.

<sup>6</sup> Center for Oceanographic Research COPAS Coastal,
Universidad de Concepción, Chile

This document reproduces and supports all data work and statistical
analysis of the larval survival, geometric morphometrics and swimming
activity in the paper **"The effects of acute temperature changes on the
swimming performance, survival and morphometrics of zoea 1 larvae of the
kelp crab (*Taliepus dentatus*) from Central Chile.**.

# Libraries

```{r chunk_opt, include=FALSE}
knitr::opts_chunk$set(dpi=600, message=FALSE, warning=FALSE, paged.print=FALSE)

```

```{r libraries, message=FALSE, warning=FALSE}
#Mortality libraries
library(cowplot)
library(scales)
library(dplyr)
library(gridExtra)
library(tidyverse) 
library(ggsci)
library(Rmisc)
library(survminer)
library(survival)
library(MASS)

#Morphometrics Libraries 
library(Morpho)
library(geomorph)
library(shapes)
library(StereoMorph)
library(readr)
library(ggplot2)

#Swimming libraries
library(tidyverse)
library(lme4)
library(plyr)
library(lmerTest)
library(lme4)
library(car)
library(sjPlot)
library(effects)
library(cowplot)
library(emmeans)
library(sjPlot)
library(multcomp)
library(rlist)

cbPalette <- c("#3B4992FF","#008B45FF","#EE0000FF")
```

# Timeseries of environmental temperature

```{r Timeseries_temp}
montemar<-read.table("~/Documents/GitHub/Swimming/data/timeseries/miniDOT.dat", header = FALSE)

#MAKING DATETIME COLUMN and ADDING COLUMNS GROUPS
montemar_date <- montemar %>%
  unite("date", V1:V3, sep = "-")
montemar_date$date<-anytime::anydate(montemar_date$date)

montemar_date$jd <- yday(montemar_date$date)  
montemar_date$day<-day(montemar_date$date)
montemar_date$month<-month(montemar_date$date)
montemar_date$year<-year(montemar_date$date)

#mean temperature by days
Day_temp<-montemar_date %>%        
  group_by(year,month, day) %>%   
  dplyr::summarize(mean_temp = mean(V6), SD=sd(V6))  
Day_temp<-Day_temp %>% mutate(Date = make_date(year, month, day))
Day_temp<-Day_temp[1:365,] #RUN TO TAKE ONLY FIRST YEAR (2021 JAN-2022 JAN)
Day_temp$month<-as.factor(Day_temp$month)

#mean temperature by month
Month_temp <- montemar_date %>% 
  group_by(year,month) %>%  
  dplyr::summarize(mean_temp = mean(V6, na.rm=T), SD=sd(V6,na.rm=T), n=n())

Month_temp

ggplot(Day_temp, aes(x=Date, y=mean_temp)) + geom_point() + geom_line()+ theme_bw() + scale_x_date(date_labels = "%b", date_breaks = "1 month") + 
  geom_errorbar(aes(ymin=Day_temp$mean_temp-SD, ymax=Day_temp$mean_temp+SD), 
                width=.2, position=position_dodge(0.05),alpha=0.5) +
  labs(y="Temperature (C°)")+ theme(plot.margin = margin(0.2,0.5,0.2,0.2, "cm")) + labs(x=element_blank())
```

# Mortality

## 1. Import of data base and definition of factors

```{r mort_data}
#data are available in the online version of the article, write your own filepath
Mort<-read.delim("~/Documents/GitHub/Swimming/data/mortality/mort.txt")
Mort$bino<-Mort$alive/100

#Temperature as factor
Mort$Temperature<-as.factor(Mort$Temperature)
```

## 2. Data summary

```{r mort_summ}
# SD, SE, CI and  MEAN
LT50_summary<- summarySE(Mort, measurevar="bino",
                         groupvars=c("Temperature","Day"))
head(LT50_summary)
```

## 3. Generalized Lineal Model (GLM) analysis and LT50%

```{r glm_lt50}

#separation of the table by temp 
mort_12<-LT50_summary[1:11, ]
mort_15<-LT50_summary[12:22, ]
mort_17<-LT50_summary[23:32,]

#GLM analysis for 12°C
model1<-glm(data=mort_12, bino ~ Day, family=quasibinomial())
summary(model1)

#GLM analysis for 15°C
model2<-glm(data=mort_15, bino ~ Day, family=quasibinomial())
summary(model2)

#GLM analysis for 17°C
model3<-glm(data=mort_17, bino ~ Day, family=quasibinomial())
summary(model3)

#Dose.p function to find moment at which 50% of the population has died (LT50%) based in the glm models made above

#LT50% for 12°C
dose.p(model1, p = 0.5)

#LT50% for 15°C
dose.p(model2, p = 0.5)

#LT50% for 17°C
dose.p(model3, p = 0.5)

# LT50% values with their CI
lt50<-c(4.531844, 6.493628, 5.919705)
CI<-c(0.6121778*1.95, 0.11405*1.95, 0.2142654*1.95)
temp<-c(12, 15,17)
data_final<-data.frame(temp,lt50, CI)
data_final$temp<-as.factor(data_final$temp)
data_final

```

## 4. Kaplan-Meier Analysis

```{r KAP_MEI}

#Vector for creating correct data table
repV<- Mort$dead 
  repV[repV=="0"]<-1

#Datatable KAP for analysis
KAP<-Mort %>%
  mutate(count = repV) %>%
  uncount(count)

# Adding Status column (binary in which 1=no death; 2=death on that day)
KAP$STATUS <- ifelse (KAP$dead==0, 1, 2)
survObj <- Surv(time=KAP$Day, event=KAP$STATUS==2)

#Kaplan-Meier analysis 
sfit <- survfit(Surv(Day, STATUS)~Temperature, data=KAP)
summary(sfit)
#Ploting Kaplan-meier results
ggsurvplot(sfit, conf.int=TRUE, pval=TRUE, risk.table=FALSE, 
           legend.labs=c("12°C", "15°C","17°C"),
           legend.title="Temperature", 
           risk.table.height=.15, ylab="Survival", xlab="Day", palette = cbPalette, font.x=9, font.y=9, font.tickslab=8,font.legend=9, break.x.by=1, pval.size=3,legend="right")
ggsave("/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/ZoeaSurv.pdf",dpi = 600, width = 2800, height = 1900, units = "px")

```

*Fig 1. Kaplan-meier survival curve (lines) for each temperature with
their confidence interval (shaded color)*

------------------------------------------------------------------------

# Geometric Morphometrics and Distance-Base Analysis.

## Digitizing

```{r digi_data}
curve.v1<- c("organo_dorsal","esq_izq_caparaza")
curve.v2<- c("punta_espina_dorsal","punta_espina_dorsal")
curve.v3<- c("curvaD_espina_dorsal","curvaI_espina_dorsal")
curve<- matrix(c(curve.v3,curve.v2, curve.v1), ncol = 3)

# take-off "#" of the digitizeimages function in order to visualize each picture digitalization on rmarkdown. 

#digitizeImages(image.file="data/morphometrics/ZOEA1_FOTOS/12°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea1")
#digitizeImages(image.file="data/morphometrics/ZOEA1_FOTOS/15°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea1")
#digitizeImages(image.file="data/morphometrics/ZOEA1_FOTOS/17°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea1")

#digitizeImages(image.file="data/morphometrics/ZOEA8_FOTOS/12°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea8")
#digitizeImages(image.file="data/morphometrics/ZOEA8_FOTOS/15°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea8")
#digitizeImages(image.file="data/morphometrics/ZOEA8_FOTOS/17°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea8")

```

## 1. Import Digitized pictures, grouping files and links for landmarks

```{r geom_data}
zoea1<-readShapes("~/Documents/GitHub/Swimming/data/morphometrics/zoea1")
zoea8<-readShapes("~/Documents/GitHub/Swimming/data/morphometrics/zoea8")

array_data_zoea1<-readland.shapes(zoea1, nCurvePts= c(7,7))
array_data_zoea8<-readland.shapes(zoea8, nCurvePts= c(7,7))

trait1<- read_delim("~/Documents/GitHub/Swimming/data/morphometrics/trait1.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
trait8<- read_delim("~/Documents/GitHub/Swimming/data/morphometrics/trait8.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)


linkscva<-list(c(1,8:8,9:9,10:10,11:11,12:12,7),c(3,5:4,5:4,6:6,3),c(1,13:13,14:14,15:15,16:16,17:17,2))
linksgeo <- read_delim("~/Documents/GitHub/Swimming/data/morphometrics/links.txt", delim = "\t", 
                       escape_double = FALSE, col_names = FALSE, 
                       trim_ws = TRUE)
linksgeo<-as.matrix(linksgeo)
trait1$Temp<- as.factor(trait1$Temp)
trait1$Replica<-as.factor(trait1$Replica)
trait1$Dia<-as.factor(trait1$Dia)
trait8$Temp<- as.factor(trait8$Temp)
trait8$Replica<-as.factor(trait8$Replica)
trait8$Dia<-as.factor(trait8$Dia)

```

## 2. Distance of the Spine length.

```{r spine_plot}
# Classic measure, dorsal spinal distance 
zoea_DSpine <- c()
for(i in 1:length(array_data_zoea1[["landmarks"]])){
  r <- sum(distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][1,],array_data_zoea1[["landmarks"]][[i]][4,]),
           distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][4,],array_data_zoea1[["landmarks"]][[i]][5,]),
           distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][5,],array_data_zoea1[["landmarks"]][[i]][6,]),
           distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][6,],array_data_zoea1[["landmarks"]][[i]][7,]))
  zoea_DSpine <- c(zoea_DSpine,r)
}


zoea1_DSpine <- data.frame(zoea_DSpine, trait1)


zoea_DSpine <- c()
for(i in 1:length(array_data_zoea8[["landmarks"]])){
  r <- sum(distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][1,],array_data_zoea8[["landmarks"]][[i]][4,]),
           distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][4,],array_data_zoea8[["landmarks"]][[i]][5,]),
           distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][5,],array_data_zoea8[["landmarks"]][[i]][6,]),
           distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][6,],array_data_zoea8[["landmarks"]][[i]][7,]))
  zoea_DSpine <- c(zoea_DSpine,r)
}
zoea8_DSpine <- data.frame(zoea_DSpine, trait8)

zoea_DSpine_F <- rbind(zoea1_DSpine,zoea8_DSpine)

zoea_DSpine_F <- zoea_DSpine_F %>% group_by(Dia,Temp,Replica) %>% dplyr::summarise(zoea_DSpine_mean=mean(zoea_DSpine),zoea_DSpine_sd=sd(zoea_DSpine))

ggplot(zoea_DSpine_F, aes(x=Temp, y=zoea_DSpine_mean, fill=Dia)) + geom_boxplot()+ theme_classic() + labs(x="Temperature (°C)", y="Dorsal spine length (mm)", fill="Day") + scale_fill_aaas() + theme(text = element_text(size = 7))

```

## 3. Generalized Procrustes Analysis (GPA)

```{r GPA}
GPA_zoea1<- gpagen(array_data_zoea1,ProcD=FALSE, print.progress = FALSE, curves = array_data_zoea1$curves) #procD=false, bending energy is the correct criterion for optimizing the positions of semilandmarks
gdf_zoea1<- geomorph.data.frame(GPA_zoea1, Temp=trait1$Temp, horas= trait1$Horas, replica=trait1$Replica, Dia=trait1$Dia)
summary(GPA_zoea1)

GPA_zoea8<- gpagen(array_data_zoea8,ProcD=FALSE, print.progress = FALSE, curves = array_data_zoea8$curves) #procD=false, bending energy is the correct criterion for optimizing the positions of semilandmarks
gdf_zoea8<- geomorph.data.frame(GPA_zoea8, Temp=trait8$Temp, horas= trait8$Horas, replica=trait8$Replica, Dia=trait8$Dia)
summary(GPA_zoea8)

plotAllSpecimens(GPA_zoea1$coords, links = linksgeo, plot.param = list(txt.cex = 1.5, txt.col = "#D53E4F", pt.bg = "#BDBDBD", link.col = "black", mean.bg = "black"))
mzoea1 <- mshape(GPA_zoea1$coords)
plot(mzoea1, links = linksgeo)
plotAllSpecimens(GPA_zoea8$coords, links = linksgeo, plot.param = list(txt.cex = 1.5, txt.col = "#D53E4F", pt.bg = "#BDBDBD", link.col = "black", mean.bg = "black"))
mzoea8 <- mshape(GPA_zoea8$coords)
plot(mzoea8, links = linksgeo)
```

## 4. Principal Components Analysis (PCA)

```{r PCA}
PCA_zoea1<-gm.prcomp(GPA_zoea1$coords)
df_zoea1 <- as.data.frame(PCA_zoea1$x)
df_zoea1 <- data_frame(df_zoea1, trait1)
df_zoea1 <- df_zoea1 %>% group_by(Temp, Replica) %>% mutate(across(everything(),mean))
pca_zoea1<-ggplot(data=df_zoea1, aes(x=Comp1, y=Comp2, col=df_zoea1$Temp)) + geom_point(size=3) + theme_classic() + labs(x="PC1=34%", y="PC2=20%", shape="Día", col="Temperature")+ scale_colour_manual(cbPalette)
summaryPCA1<-summary(PCA_zoea1)

PCA_zoea8<-gm.prcomp(GPA_zoea8$coords)
df_zoea8 <- as.data.frame(PCA_zoea8$x)
df_zoea8 <- data_frame(df_zoea8, trait8)
df_zoea8 <- df_zoea8 %>% group_by(Temp, Replica) %>% mutate(across(everything(),mean))
pca_zoea8<-ggplot(data=df_zoea8, aes(x=Comp1, y=Comp2, col=df_zoea8$Temp)) + geom_point(size=3) + theme_classic() + labs(x="PC1=52%", y="PC2=15%", shape="Día", col="Temperature")+ scale_colour_aaas()
summaryPCA8<-summary(PCA_zoea8)

# Mean shape against max or minimun shape of Principal components
pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc1max_zoea1.pdf", width = 4, height = 4)
pc1max_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp1$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc1min_zoea1.pdf", width = 4, height = 4)
pc1min_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp1$min,method = "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc2max_zoea1.pdf", width = 4, height = 4)
pc2max_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp2$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc2min_zoea1.pdf", width = 4, height = 4)
pc2min_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp2$min,method = "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc1max_zoea8.pdf", width = 4, height = 4)
pc1max_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp1$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc1min_zoea8.pdf", width = 4, height = 4)
pc1min_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp1$min,method = "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc2max_zoea8.pdf", width = 4, height = 4)
pc2max_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp2$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/pc2min_zoea8.pdf", width = 4, height = 4)
pc2min_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp2$min,method = "points", links = linksgeo)
dev.off()


```


## 5. Canonical Variance Analysis (CVA)

```{r CVA}

# Column to the Database to later use as grouping
trait1$grouppp<-paste(trait1$Temp, trait1$Day)
trait8$grouppp<-paste(trait8$Temp, trait8$Day)

# Canonical variance analysis using bonferroni p-value adjustment 
cva1<-CVA(GPA_zoea1$coords, groups = trait1$Temp, p.adjust.method = "bonferroni",rounds = 9999, robust = "classical")
cva8<-CVA(GPA_zoea8$coords, groups = trait8$Temp, p.adjust.method = "bonferroni",rounds = 9999, robust = "classical")

# P-values (euclides) obtained between groups of permutation test (9999)
(cva1[["Dist"]][["probsEuclid"]])
(cva8[["Dist"]][["probsEuclid"]])

Cva_out_1<-as.data.frame(cva1$CVscores)
consensus_1<-as.data.frame(cva1$groupmeans)
Cva_out_1$temp<-gdf_zoea1$Temp
cva1_plot <- ggplot(data=Cva_out_1, aes(x=`CV 1`, y=`CV 2`, col=temp)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
  labs(x="CV 1", y= "CV 2", col= "Temperature") + theme_classic() + scale_colour_manual(values=cbPalette)

Cva_out_8<-as.data.frame(cva8$CVscores)
consensus_8<-as.data.frame(cva8$groupmeans)
Cva_out_8$temp<-gdf_zoea8$Temp
cva8_plot <-ggplot(data=Cva_out_8, aes(x=`CV 1`, y=`CV 2`, col=temp)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
  labs(x="CV 1", y= "CV 2", col= "Temperature") + theme_classic() + scale_colour_manual(values=cbPalette)

shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==12 & zoea_DSpine_F$Dia==1])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==15 & zoea_DSpine_F$Dia==1])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==17 & zoea_DSpine_F$Dia==1])

shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==12 & zoea_DSpine_F$Dia==8])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==15 & zoea_DSpine_F$Dia==8])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==17 & zoea_DSpine_F$Dia==8])

mod1 <- aov(zoea_DSpine_mean~Temp*Dia, data = zoea_DSpine_F)
anova(mod1)

posteriori<- TukeyHSD(mod1, which = "Temp:Dia")
posteriori[["Temp:Dia"]][,4]<0.05

plot(posteriori)
```

------------------------------------------------------------------------

# Swimming Performance

## 1. Import database and Tyding

```{r swimm_data}
#data are available in the online version of the article, write your own filepath
list_of_files <- list.files(path = "~/Documents/GitHub/Swimming/data/swimming", recursive = TRUE,pattern = "\\.txt$", full.names = TRUE)

#Lapply allows to import all the files in one list
loop_full<-lapply(list_of_files, read.delim2)
names(loop_full)<-list_of_files
loop_full<-lapply(loop_full, function(x) { x["frame"] <- NULL; x })
```

```{r 12_loop}
mean_t1_12<-list()
# for loop to make same functions to all files of 12°C 
for (i in 1:14){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2] #Mean velocity by larvae
mean_t1_12[[i]]<-z1
}
names(mean_t1_12)<-list_of_files[1:14] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_12<-Map(cbind, mean_t1_12, group = names(mean_t1_12))
mean_t1_12<- list.rbind(mean_t1_12)
mean_t1_12<-mean_t1_12 %>% separate(group, c("a", "B","C","D","e","f","g","h","i","j","k","l","m","n","o","p","q","r","s"))
mean_t1_12<-mean_t1_12[,c(16,17,18,1,2,3)]
colnames(mean_t1_12)<-c("Temp","aquarium","Larva","Trajectory","Time","IV")
```

```{r 15_loop}
mean_t1_15<-list()
# for loop to make same functions to all files of 15°C 
for (i in 15:25){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity 
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2] #Mean velocity by larvae
mean_t1_15[[i]]<-z1
}
mean_t1_15<-mean_t1_15[c(15:25)]
names(mean_t1_15)<-list_of_files[15:25] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_15<-Map(cbind, mean_t1_15, group = names(mean_t1_15))
mean_t1_15<- list.rbind(mean_t1_15)
mean_t1_15<-mean_t1_15 %>% separate(group, c("a", "B","C","D","e","f","g","h","i","j","k","l","m","n","o","p","q","r","s"))
mean_t1_15<-mean_t1_15[,c(15,16,17,1,2,3)]
colnames(mean_t1_15)<-c("Temp","aquarium","Larva","Trajectory","Time","IV")
```

```{r 17_loop}
mean_t1_17<-list()
# for loop to make same functions to all files of 17°C 
for (i in 26:39){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity 
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2] #Mean velocity by larvae
mean_t1_17[[i]]<-z1
}
mean_t1_17<-mean_t1_17[c(26:39)]
names(mean_t1_17)<-list_of_files[26:39] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_17<-Map(cbind, mean_t1_17, names = names(mean_t1_17))
mean_t1_17<- list.rbind(mean_t1_17) 
mean_t1_17<-mean_t1_17 %>% separate(names, c("a", "B","C","D","e","f","g","h","i","j","k","l","m","n","o","p","q","r","s"))
mean_t1_17<-mean_t1_17[,c(15,16,17,1,2,3)]
colnames(mean_t1_17)<-c("Temp","aquarium","Larva","Trajectory","Time","IV")
data<-rbind(mean_t1_12,mean_t1_15,mean_t1_17)
```

```{r swimm_tidy}
#Tidying data
data1<-data%>%group_by(Temp,aquarium,Larva) %>%
  dplyr::summarise(Ist_Vel = mean(IV),
                   Tot_Time= sum(Time), Max_Time=max(Time))%>%rowid_to_column(var='ID')
data1$Temp<-as.factor(data1$Temp)
```

```{r Median_swimm}
#Median of instant velocity by temp
medIV <- ddply(data1, "Temp", summarise, grp.med=median(Ist_Vel), Q1=quantile(Ist_Vel, c(0.25), type = 6),Q3=quantile(Ist_Vel, c(0.75), type = 6), IQR=Q3-Q1)
print(medIV)
#Median of max time swimming by temp
medMax <- ddply(data1, "Temp", summarise, grp.med=median(Max_Time),
Q1=quantile(Max_Time, c(0.25), type = 6),Q3=quantile(Max_Time, c(0.75), type = 6), IQR=Q3-Q1)
print(medMax)
```

## 2. Kernel plots

```{r Kernel_IV}
#Non-parametric Kernel Densities plot for instant velocity (IV)
dplot_IV<-ggplot(data1, aes(Ist_Vel, color=Temp))+
  geom_density(kernel = "gaussian")+ 
  geom_point(aes(x=5.13, y=0),colour="#3B4992FF",shape=17, size=7)+
  geom_point(aes(x=1.76, y=0),colour="#008B45FF",shape=17, size=7)+
  geom_point(aes(x=1.56, y=0),colour="#EE0000FF",shape=17, size=7)+
  theme_classic()+ 
  labs(colour="Temperature (°C)", x="Instant Velocity (mm/s)", y="Kernel density")+ 
  scale_x_continuous(limits = c(0, NA),breaks = 0:10, expand = expansion(mult = c(0, 0.1))) +
  scale_y_continuous(limits = c(0, NA),breaks =seq(from=0,to=1, by=0.1),
expand = expansion(mult = c(0, 0.1))) +
  theme(text = element_text(size = 10)) +
  scale_colour_manual(values=cbPalette)
dplot_IV
```

*Kernel density plot of instant velocity (IV) with their median
(triangle) by temperature*

```{r Kernel_MT}
#Non-parametric Kernel Densities plot for max time swimming (MT)
dplot_Max<-ggplot(data1, aes(Max_Time, color=Temp))+
  geom_density(kernel="gaussian")+
  geom_point(aes(x=10.25, y=0),color="#3B4992FF",shape=17, size=7)+
  geom_point(aes(x=18.80, y=0),color="#008B45FF",shape=17, size=7)+
  geom_point(aes(x=19.25, y=0),color="#EE0000FF",shape=17, size=7)+
  theme_classic()+
  labs(colour="Temperature (°C)", x="Max Time Swimming (sec)", y="Kernel density")+ 
  scale_x_continuous(limits = c(0, NA),breaks = seq(from=0,to=50,by=5),expand = expansion(mult = c(0, 0.1))) +
  scale_y_continuous(limits = c(0, NA),breaks = seq(from=0,to=0.06,by=0.01),expand = expansion(mult = c(0, 0.1))) +
  theme(text = element_text(size = 10)) +
  scale_colour_manual(values = cbPalette)
dplot_Max
```

*Kernel density plot of max time swimming (MT) with their median
(triangle) by temperature*

## 3. Linear mixed effects model with log transformed data

```{r lm_assmptn}
#Checking for normality
shapiro.test(log(data1$Ist_Vel))
hist(log(data1$Ist_Vel))
shapiro.test(log(data1$Max_Time))
hist(log(data1$Max_Time))

#Checking for heteroscedasticity
leveneTest(log(data1$Ist_Vel), data1$Temp)
leveneTest(log(data1$Max_Time),data1$Temp)

```

```{r swimm_lm}
#Linear mixed effects model with Log transformed data of IV. aquarium is a factor with random effects and larva is nested in aquarium 
modIV<-lmer(log(Ist_Vel)~Temp + (aquarium|Larva), data=data1)
summary(modIV)
anova(modIV)
#model diagnostic
plot(modIV,which = 1)
qqnorm(resid(modIV))
qqline(resid(modIV))


#Linear mixed effects model with Log transformed data of MT aquarium is a factor with random effects and larva is nested in aquarium 
modMax<-lmer(log(Max_Time)~Temp + (aquarium|Larva), data=data1)
summary(modMax)
anova(modMax)
#model diagnostic
plot(modMax,which = 1)
qqnorm(resid(modMax))
qqline(resid(modMax))

```

## 4. Pairwise comparisions and log transformed data plots

```{r swimm_pw}
#pairwise comparison using estimated means of instant velocity by temp
meansIV<-emmeans(modIV, pairwise ~ Temp, adjust="bonferroni")
meansIV

#pairwise comparison using estimated means of max time swimming by temp
meansMax<-emmeans(modMax, pairwise ~ Temp, adjust="bonferroni")
meansMax
```

## 5. Plots

```{r logIV_plot}
#Boxplot of logaritmic IV data 
p1<-ggplot(data1, aes(x=Temp, y=log(Ist_Vel), fill=Temp))+geom_boxplot(outliers = F)+
  stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") +
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic()+labs(x="Temperature (°C)", y="IV")+theme(legend.position="none",text= element_text(size=10))+
   scale_fill_manual(values = cbPalette)+ 
  scale_y_continuous(breaks =c(1,2,0))+  geom_text(x=1.2,y=2.4,label="a",color="red", size = 3)+
  geom_text(x=2.2,y=1.4,label="b",color="red", size = 3)+
  geom_text(x=3.2,y=1.4,label="b",color="red", size = 3)
p1
```

*Boxplot that represents logarithmic AIV distribution of the data by
temperature, letters indicate significant difference.*

```{r logMT_plot}
# Boxplot of logaritmic MT data 
p2<-ggplot(data1, aes(x=Temp, y=log(Max_Time), fill=Temp))+
  geom_boxplot()+ stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") + 
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic() + theme(legend.position="none",text= element_text(size=10)) +
  labs(x="Temperature (°C)", y="MTS")+
   scale_fill_manual(values=cbPalette)+
  geom_text(x=1.2,y=3.2,label="a",color="red",size = 3)+
  geom_text(x=2.2,y=3.7,label="a",color="red",size = 3)+
  geom_text(x=3.2,y=3.7,label="a",color="red",size = 3)+ scale_y_continuous(breaks = 0:4)
p2

```

*Boxplot that represents logarithmic MTS distribution of the data by
temperature, letters indicate significant difference.*

```{r IV_plot}
#kernel density plot with inset boxplot of IV
plot.with.inset.IV <-
  ggdraw() +
  draw_plot(dplot_IV) +
  draw_plot(p1, x = .35, y = 0.65, width = .3, height = .35)
plot.with.inset.IV
ggsave("/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/IVKernel.pdf",dpi = 600, width = 2800, height = 1900, units = "px")

```


```{r MT_plot}
#kernel density plot with inset boxplot of MT
plot.with.inset.Max_Time <-
  ggdraw() +
  draw_plot(dplot_Max) +
  draw_plot(p2, x = .35, y = 0.65, width = .3, height = .35)
plot.with.inset.Max_Time
ggsave("/Users/lucasb/Desktop/ECOLAB!/paper tesis/FIGURES PAPER/plots R/MTSKernel.pdf",dpi = 600, width = 2500, height = 1900, units = "px")


```

