---
title: Supplementary data 1
subtitle: "Reproducible report"
author: Lucas Bravo<sup>1</sup>, Milena Cano<sup>1</sup>, Mauricio F. Landaeta<sup>2,3</sup>, Sergio Navarrete<sup>4,5,6</sup>, Simone Baldanzi<sup>1,2</sup>
output: 
 html_document:
   keep_md: yes
---

<sup>1</sup> Laboratorio de Ecofisiología y Ecología Evolutiva Marina
(e°CO2lab), Facultad de Ciencias del mar y de Recursos Naturales,
Universidad de Valparaíso, Viña del Mar, Chile.

<sup>2</sup> Centro de Observación Marino para Estudios de Riesgos del
Ambiente Costero (COSTA-R), Universidad de Valparaíso, Chile

<sup>3</sup> Laboratorio de Ictiología e Interacciones Biofíscas
(LABITI), Facultad de Ciencias, Universidad de Valparaíso, Valparaiso,
Chile

<sup>4</sup> Estación Costera de Investigaciones Marinas (ECIM),
Pontificia Universidad Católica de Chile, Las Cruces, Chile.

<sup>5</sup> Center for Applied Ecology and Sustainability (CAPES), and
Instituto Milenio en Socioecología Costera, SECOS, Pontificia
Universidad Católica de Chile, Santiago, Chile.

<sup>6</sup> Center for Oceanographic Research COPAS Coastal,
Universidad de Concepción, Chile

This document reproduces and supports all data work and statistical
analysis of the larval survival, geometric morphometrics and swimming
activity in the paper **"Assessing the effect of acute temperature
changes on the swimming performance, survival and morphometrics of zoea
larvae of the kelp crab *Taliepus dentatus*"**.


```{r chunk_opt, include=FALSE}
knitr::opts_chunk$set(dpi=600, message=FALSE, warning=FALSE, paged.print=FALSE)

```

# Libraries

```{r libraries}
#Mortality libraries
library(cowplot)
library(scales)
library(dplyr)
library(gridExtra)
library(tidyverse) 
library(ggsci)
library(Rmisc)
library(survminer)
library(survival)
library(MASS)

#Morphometrics Libraries 
library(Morpho)
library(geomorph)
library(shapes)
library(StereoMorph)
library(readr)
library(ggplot2)
library(writexl)

#Swimming libraries
library(lme4)
library(plyr)
library(lmerTest)
library(lme4)
library(car)
library(sjPlot)
library(effects)
library(cowplot)
library(emmeans)
library(sjPlot)
library(multcomp)
library(rlist)

cbPalette <- c("#3B4992FF","#008B45FF","#EE0000FF")
```

# Timeseries of environmental temperature

```{r Timeseries_temp}
montemar<-read.table("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/data/timeseries/miniDOT.dat", header = FALSE)

#MAKING DATETIME COLUMN and ADDING COLUMNS GROUPS
montemar_date <- montemar %>%
  unite("date", V1:V3, sep = "-")
montemar_date$date<-anytime::anydate(montemar_date$date)

montemar_date$jd <- yday(montemar_date$date)  
montemar_date$day<-day(montemar_date$date)
montemar_date$month<-month(montemar_date$date)
montemar_date$year<-year(montemar_date$date)

#mean temperature by days
Day_temp<-montemar_date %>%        
  group_by(year,month, day) %>%   
  dplyr::summarize(mean_temp = mean(V6), SD=sd(V6), min_temp=min(V6), max_temp=max(V6))  
Day_temp<-Day_temp %>% mutate(Date = make_date(year, month, day))
Day_temp<-Day_temp[1:365,] #RUN TO TAKE ONLY FIRST YEAR (2021 JAN-2022 JAN)
Day_temp$month<-as.factor(Day_temp$month)

#mean temperature by month
Month_temp <- montemar_date %>% 
  group_by(year,month) %>%  
  dplyr::summarize(mean_temp = mean(V6, na.rm=T), SD=sd(V6,na.rm=T), n=n())

Month_temp

ggplot(Day_temp, aes(x=Date, y=mean_temp,ymin=Day_temp$min_temp, ymax=Day_temp$max_temp))+ geom_ribbon(fill = "black", alpha = 0.4) + geom_line(color="black")+ theme_bw() + scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(y="Temperature (C°)")+ theme(plot.margin = margin(0.2,0.5,0.2,0.2, "cm")) + labs(x=element_blank()) 
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/timeseries.pdf", dpi=600)
```

# Mortality

## 1. Import of data base and definition of factors

```{r mort_data}
#data are available in the online version of the article, write your own filepath
Mort<-read.delim("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/data/mortality/mort 2.txt")
Mort$bino<-Mort$alive/100

#Temperature as factor
Mort$Temperature<-as.factor(Mort$Temperature)
```

## 2. Data summary

```{r mort_summ}
# SD, SE, CI and  MEAN
LT50_summary<- summarySE(Mort, measurevar="bino",
                         groupvars=c("Temperature","Day"))
head(LT50_summary)
```

## 3. Generalized Lineal Model (GLM) analysis and LT50%

```{r glm_lt50}

#separation of the table by temp 
mort_12<-LT50_summary[1:11, ]
mort_15<-LT50_summary[12:22, ]
mort_17<-LT50_summary[23:32,]

#GLM analysis for 12°C
model1<-glm(data=mort_12, bino ~ Day, family=quasibinomial())
summary(model1)

#GLM analysis for 15°C
model2<-glm(data=mort_15, bino ~ Day, family=quasibinomial())
summary(model2)

#GLM analysis for 17°C
model3<-glm(data=mort_17, bino ~ Day, family=quasibinomial())
summary(model3)

#Dose.p function to find moment at which 50% of the population has died (LT50%) based in the glm models made above

#LT50% for 12°C
dose.p(model1, p = 0.5)

#LT50% for 15°C
dose.p(model2, p = 0.5)

#LT50% for 17°C
dose.p(model3, p = 0.5)

# LT50% plot with values given by dose.p

lt50<-c(4.531844, 6.493628, 5.919705)
CI<-c(0.6121778*1.95, 0.11405*1.95, 0.2142654*1.95)
temp<-c(12, 15,17)
data_final<-data.frame(lt50, CI, temp)
data_final$temp<-as.factor(data_final$temp)


lt50_plot<-ggplot(data_final, aes(x=temp, y=lt50, fill=temp, shape=temp))+ 
  geom_bar(stat="identity") + theme_classic() + scale_y_continuous(breaks = 1:7) +
  labs( x="", y="LT50% (days)", fill= "Temperature(°C)") + 
  scale_fill_manual(values =c(cbPalette),
                    labels=c("12","15","17")) 
lt50_plot + geom_errorbar(aes(ymin=lt50-CI, ymax=lt50+CI), width=.2, position=position_dodge(0.05)) #+
  #geom_text(aes(x=temp,y=lt50,label=c("4.50","6.50","5.90")),position =position_dodge(width = 1), hjust=1.8, vjust=-0.2) 

#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/LT50.pdf",dpi = 600)

```

## 4. Kaplan-Meier Analysis

```{r KAP_MEI}

#Vector for creating correct data table
repV<- Mort$dead 
  repV[repV=="0"]<-1

#Datatable KAP for analysis
KAP<-Mort %>%
  mutate(count = repV) %>%
  uncount(count)

# Adding Status column (binary in which 1=no death; 2=death on that day)
KAP$STATUS <- ifelse (KAP$dead==0, 1, 2)
survObj <- Surv(time=KAP$Day, event=KAP$STATUS==2)

#Kaplan-Meier analysis 
sfit <- survfit(Surv(Day, STATUS)~Temperature, data=KAP)
summary(sfit)
#Ploting Kaplan-meier results
ggsurvplot(sfit, conf.int=TRUE, pval=TRUE, risk.table=FALSE, 
           legend.labs=c("12", "15","17"),
           legend.title="Temperature(°C)", 
           risk.table.height=.15, ylab="Starvation Survival", xlab="Day", palette = cbPalette, font.x=9, font.y=9, font.tickslab=8,font.legend=9, break.x.by=1, pval.size=3,legend="right")
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/ZoeaSurv.pdf",dpi = 600, width = 2800, height = 1900, units = "px")

```

*Fig 1. Kaplan-meier survival curve (lines) for each temperature with
their confidence interval (shaded color)*

------------------------------------------------------------------------

# Geometric Morphometrics and Distance-Base Analysis.

## Digitizing

```{r digi_data}
curve.v1<- c("organo_dorsal","esq_izq_caparaza")
curve.v2<- c("punta_espina_dorsal","punta_espina_dorsal")
curve.v3<- c("curvaD_espina_dorsal","curvaI_espina_dorsal")
curve<- matrix(c(curve.v3,curve.v2, curve.v1), ncol = 3)

# take-off "#" of the digitizeimages function in order to visualize each picture digitalization on rmarkdown. 

#digitizeImages(image.file="data/morphometrics/ZOEA1_FOTOS/12°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea1")
#digitizeImages(image.file="data/morphometrics/ZOEA1_FOTOS/15°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea1")
#digitizeImages(image.file="data/morphometrics/ZOEA1_FOTOS/17°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea1")

#digitizeImages(image.file="data/morphometrics/ZOEA8_FOTOS/12°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea8")
#digitizeImages(image.file="data/morphometrics/ZOEA8_FOTOS/15°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea8")
#digitizeImages(image.file="data/morphometrics/ZOEA8_FOTOS/17°C", landmarks.ref="data/morphometrics/landmarks.txt", curves.ref = curve, shapes.file ="data/morphometrics/zoea8")

```

## 1. Import Digitized pictures, grouping files and links for landmarks

```{r geom_data}
zoea1<-readShapes("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Data/morphometrics/zoea1")
zoea8<-readShapes("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Data/morphometrics/zoea8")

array_data_zoea1<-readland.shapes(zoea1, nCurvePts= c(7,7))
array_data_zoea8<-readland.shapes(zoea8, nCurvePts= c(7,7))

trait1<- read_delim("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Data/morphometrics/trait1.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
trait8<- read_delim("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Data/morphometrics/trait8.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)


linksgeo <- read_delim("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Data/morphometrics/links.txt", delim = "\t", 
                       escape_double = FALSE, col_names = FALSE, 
                       trim_ws = TRUE)
linksgeo<-as.matrix(linksgeo)
trait1$Temp<- as.factor(trait1$Temp)
trait1$Replica<-as.factor(trait1$Replica)
trait1$Dia<-as.factor(trait1$Dia)
trait8$Temp<- as.factor(trait8$Temp)
trait8$Replica<-as.factor(trait8$Replica)
trait8$Dia<-as.factor(trait8$Dia)

```

## 2. Distance of the Spine length.

```{r spine_plot}
# Classic measure, dorsal spinal distance 
zoea_DSpine <- c()
for(i in 1:length(array_data_zoea1[["landmarks"]])){
  r <- sum(distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][1,],array_data_zoea1[["landmarks"]][[i]][4,]),
           distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][4,],array_data_zoea1[["landmarks"]][[i]][5,]),
           distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][5,],array_data_zoea1[["landmarks"]][[i]][6,]),
           distancePointToPoint(array_data_zoea1[["landmarks"]][[i]][6,],array_data_zoea1[["landmarks"]][[i]][7,]))
  zoea_DSpine <- c(zoea_DSpine,r)
}


zoea1_DSpine <- data.frame(zoea_DSpine, trait1)


zoea_DSpine <- c()
for(i in 1:length(array_data_zoea8[["landmarks"]])){
  r <- sum(distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][1,],array_data_zoea8[["landmarks"]][[i]][4,]),
           distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][4,],array_data_zoea8[["landmarks"]][[i]][5,]),
           distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][5,],array_data_zoea8[["landmarks"]][[i]][6,]),
           distancePointToPoint(array_data_zoea8[["landmarks"]][[i]][6,],array_data_zoea8[["landmarks"]][[i]][7,]))
  zoea_DSpine <- c(zoea_DSpine,r)
}
zoea8_DSpine <- data.frame(zoea_DSpine, trait8)

zoea_DSpine_F <- rbind(zoea1_DSpine,zoea8_DSpine)

zoea_DSpine_F <- zoea_DSpine_F %>% group_by(Dia,Temp,Replica) %>% dplyr::summarise(zoea_DSpine_mean=mean(zoea_DSpine),zoea_DSpine_sd=sd(zoea_DSpine))

ggplot(zoea_DSpine_F, aes(x=Temp, y=zoea_DSpine_mean, fill=Dia)) + geom_boxplot()+ theme_classic() + labs(x="Temperature (°C)", y="Dorsal spine length (mm)", fill="Day") + scale_fill_aaas() + theme(text = element_text(size = 7))
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/figuras/Dspine.pdf", dpi = 600)

```

## 3. Generalized Procrustes Analysis (GPA)

```{r GPA}
GPA_zoea1<- gpagen(array_data_zoea1,ProcD=FALSE, print.progress = FALSE, curves = array_data_zoea1$curves) #procD=false, bending energy is the correct criterion for optimizing the positions of semilandmarks
gdf_zoea1<- geomorph.data.frame(GPA_zoea1, Temp=trait1$Temp, horas= trait1$Horas, replica=trait1$Replica, Dia=trait1$Dia)
summary(GPA_zoea1)

GPA_zoea8<- gpagen(array_data_zoea8,ProcD=FALSE, print.progress = FALSE, curves = array_data_zoea8$curves) #procD=false, bending energy is the correct criterion for optimizing the positions of semilandmarks
gdf_zoea8<- geomorph.data.frame(GPA_zoea8, Temp=trait8$Temp, horas= trait8$Horas, replica=trait8$Replica, Dia=trait8$Dia)
summary(GPA_zoea8)

plotAllSpecimens(GPA_zoea1$coords, links = linksgeo, plot.param = list(txt.cex = 1.5, txt.col = "#D53E4F", pt.bg = "#BDBDBD", link.col = "black", mean.bg = "black"))
mzoea1 <- mshape(GPA_zoea1$coords)
plot(mzoea1, links = linksgeo)
plotAllSpecimens(GPA_zoea8$coords, links = linksgeo, plot.param = list(txt.cex = 1.5, txt.col = "#D53E4F", pt.bg = "#BDBDBD", link.col = "black", mean.bg = "black"))
mzoea8 <- mshape(GPA_zoea8$coords)
plot(mzoea8, links = linksgeo)
```

## 4. Principal Components Analysis (PCA)

```{r PCA}
combined_coords <- abind::abind(GPA_zoea1$coords, GPA_zoea8$coords, along = 3)
PCAFULL <- gm.prcomp(combined_coords)
DFFULL <- as.data.frame(PCAFULL$x)
DFFULL <- cbind(DFFULL,rbind(trait1, trait8))
trait1$grouppp<-paste(trait1$Temp, trait1$Dia, sep = " - ")
trait8$grouppp<-paste(trait8$Temp, trait8$Dia, sep = " - ")
DFFULL <- DFFULL %>% group_by(Temp, Replica) %>% mutate(across(everything(),mean))
DFFULL$grouppp <- c(trait1$grouppp, trait8$grouppp)
DFFULL$Temp <- as.factor(DFFULL$Temp)
DFFULL$Day <- c(trait1$Dia,trait8$Dia)
DFFULL$Day <- as.factor(DFFULL$Day)

ggplot(data=DFFULL, aes(x=Comp1, y=Comp2, col=Temp, shape=Day)) + geom_point(size=3) + theme_minimal() + labs(x="PC1=47.3%", y="PC2=22.0%", color="Temperature",shape="Day") + scale_colour_manual(values=cbPalette)

#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/PCAnew.pdf", dpi=600)

PCA_zoea1<-gm.prcomp(GPA_zoea1$coords)
df_zoea1 <- as.data.frame(PCA_zoea1$x)
df_zoea1 <- data_frame(df_zoea1, trait1)
df_zoea1 <- df_zoea1 %>% group_by(Temp, Replica) %>% mutate(across(everything(),mean))
colnames(df_zoea1)[colnames(df_zoea1) == 'Temp'] <- 'Temperature'

ggplot(data=df_zoea1, aes(x=Comp1, y=Comp2, col=Temperature, shape=Temperature)) + geom_point(size=3) + theme_classic() + labs(x="PC1=47%", y="PC2=28%", shape="Temperature(°C)", color="Temperature(°C)") + scale_colour_manual(values=cbPalette)

#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/PCA/zoea1_PCA.jpg", dpi=600)

#temp_zoea1 <- df_zoea1 %>% group_by(Temp) %>% mutate(across(everything(),mean))

summaryPCA1<-summary(PCA_zoea1)



b <- as.data.frame(PCA_zoea1[["rotation"]])
b <- cbind(rownames(b),b)
#write_xlsx(b, path = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/supplementary/eigenvectorsZOEA1.xlsx")

PCA_zoea8<-gm.prcomp(GPA_zoea8$coords)
df_zoea8 <- as.data.frame(PCA_zoea8$x)
df_zoea8 <- data_frame(df_zoea8, trait8)
df_zoea8 <- df_zoea8 %>% group_by(Temp, Replica) %>% mutate(across(everything(),mean))
ggplot(data=df_zoea8, aes(x=Comp1, y=Comp2, col=Temp, shape=Temp)) + geom_point(size=3) + theme_classic() + labs(x="PC1=48%", y="PC2=29%", shape="Temperature(°C)", color="Temperature(°C)")+ scale_colour_manual(values=cbPalette)
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/PCA/zoea8_PCA.jpg", dpi=600)
summaryPCA8<-summary(PCA_zoea8)

a <- as.data.frame(PCA_zoea8[["rotation"]])
a <- cbind(rownames(a),a)
#write_xlsx(a, path = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/supplementary/eigenvectorsZOEA8.xlsx")

# Mean shape against max or minimun shape of Principal components
pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc1max_zoea1.pdf", width = 4, height = 4)
pc1max_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp1$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc1min_zoea1.pdf", width = 4, height = 4)
pc1min_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp1$min,method = "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc2max_zoea1.pdf", width = 4, height = 4)
pc2max_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp2$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc2min_zoea1.pdf", width = 4, height = 4)
pc2min_zoea1 <- plotRefToTarget(mzoea1, PCA_zoea1$shapes$shapes.comp2$min,method = "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc1max_zoea8.pdf", width = 4, height = 4)
pc1max_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp1$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc1min_zoea8.pdf", width = 4, height = 4)
pc1min_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp1$min,method = "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc2max_zoea8.pdf", width = 4, height = 4)
pc2max_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp2$max,method =  "points", links = linksgeo)
dev.off()

pdf(file = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/pc2min_zoea8.pdf", width = 4, height = 4)
pc2min_zoea8 <- plotRefToTarget(mzoea8, PCA_zoea8$shapes$shapes.comp2$min,method = "points", links = linksgeo)
dev.off()
linksgeo

```


## 5. Canonical Variate Analysis (CVA)

```{r CVA}

# Column to the Database to later use as grouping
trait1$grouppp<-paste(trait1$Temp, trait1$Dia)
trait8$grouppp<-paste(trait8$Temp, trait8$Dia)

combined_coords <- abind::abind(GPA_zoea1$coords, GPA_zoea8$coords, along = 3)
c(trait1$grouppp, trait8$grouppp)

cva_full <- CVA(combined_coords, groups = c(trait1$grouppp, trait8$grouppp), p.adjust.method = "bonferroni",rounds = 9999, robust = "classical")

Cva_out_full<-as.data.frame(cva_full$CVscores)
consensus_full<-as.data.frame(Cva_out_full$groupmeans)
Cva_out_full$Temp<-c(trait1$Temp, trait8$Temp)
Cva_out_full$Day <- c(trait1$Dia, trait8$Dia)
ggplot(data=Cva_out_full, aes(x=`CV 1`, y=`CV 2`, col=Temp, shape=Day)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
  labs(x="CV 1", y= "CV 2", col= "Temperature") + theme_classic() + scale_colour_manual(values=cbPalette)
ggplot(data=Cva_out_full, aes(x=`CV 2`, y=`CV 3`, col=Temp, shape=Day)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
  labs(x="CV 2", y= "CV 3", col= "Temperature") + theme_classic() + scale_colour_manual(values=cbPalette)


# Canonical variance analysis using bonferroni p-value adjustment 
cva1<-CVA(GPA_zoea1$coords, groups = trait1$Temp, p.adjust.method = "bonferroni",rounds = 9999, robust = "classical")
cva8<-CVA(GPA_zoea8$coords, groups = trait8$Temp, p.adjust.method = "bonferroni",rounds = 9999, robust = "classical")

# P-values (euclides) obtained between groups of permutation test (9999)
(cva1[["Dist"]][["probsEuclid"]])
(cva8[["Dist"]][["probsEuclid"]])

Cva_out_1<-as.data.frame(cva1$CVscores)
consensus_1<-as.data.frame(cva1$groupmeans)
Cva_out_1$temp<-gdf_zoea1$Temp
ggplot(data=Cva_out_1, aes(x=`CV 1`, y=`CV 2`, col=temp)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
  labs(x="CV 1", y= "CV 2", col= "Temperature") + theme_classic() + scale_colour_manual(values=cbPalette)
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/figuras/CVA1.pdf", dpi = 600)

Cva_out_8<-as.data.frame(cva8$CVscores)
consensus_8<-as.data.frame(cva8$groupmeans)
Cva_out_8$temp<-gdf_zoea8$Temp
ggplot(data=Cva_out_8, aes(x=`CV 1`, y=`CV 2`, col=temp)) + geom_point() + stat_ellipse(level = 0.95) + coord_fixed() +
  labs(x="CV 1", y= "CV 2", col= "Temperature") + theme_classic() + scale_colour_manual(values=cbPalette)

#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/figuras/CVA8.pdf", dpi = 600)

shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==12 & zoea_DSpine_F$Dia==1])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==15 & zoea_DSpine_F$Dia==1])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==17 & zoea_DSpine_F$Dia==1])

shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==12 & zoea_DSpine_F$Dia==8])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==15 & zoea_DSpine_F$Dia==8])
shapiro.test(zoea_DSpine_F$zoea_DSpine_mean[zoea_DSpine_F$Temp==17 & zoea_DSpine_F$Dia==8])

mod1 <- aov(zoea_DSpine_mean~Temp*Dia, data = zoea_DSpine_F)
anova(mod1)

posteriori<- TukeyHSD(mod1, which = "Temp:Dia")
posteriori[["Temp:Dia"]][,4]<0.05

plot(posteriori)

## Groupmeans by temp
cbPalette <- c("#3B4992FF","#008B45FF","#EE0000FF")

shp_mn <- as.data.frame(rbind(cbind(cva1[["groupmeans"]][,,1], "12"),cbind(cva1[["groupmeans"]][,,2],"15"),cbind(cva1[["groupmeans"]][,,3],"17")))

shp_mn$V1 <- as.numeric(shp_mn$V1)
shp_mn$V2 <- as.numeric(shp_mn$V2)
shp_mn$Temperature <- as.factor(shp_mn$V3)

ggplot(shp_mn, aes(V1, V2, color=Temperature, shape=Temperature)) + geom_point() + theme_minimal() + labs(x="",y="", shape="Temperature(°C)", color="Temperature(°C)") + scale_color_manual(values = cbPalette) 

#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/CVA/CVA1.pdf", dpi = 600)

shp_mn8 <- as.data.frame(rbind(cbind(cva8[["groupmeans"]][,,1], "12"),cbind(cva8[["groupmeans"]][,,2],"15"),cbind(cva8[["groupmeans"]][,,3],"17")))

shp_mn8$V1 <- as.numeric(shp_mn8$V1)
shp_mn8$V2 <- as.numeric(shp_mn8$V2)
shp_mn8$Temperature <- as.factor(shp_mn8$V3)

ggplot(shp_mn8, aes(V1, V2, color=Temperature, shape=Temperature)) + geom_point() + theme_minimal() + labs(x="",y="", shape="Temperature(°C)", color="Temperature(°C)") + scale_color_manual(values = cbPalette)
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/morphometrics/CVA/CVA8.pdf", dpi = 600)
```

------------------------------------------------------------------------

# Swimming Performance

## 1. Import database and Tyding

```{r swimm_data}
#data are available in the online version of the article, write your own filepath
list_of_files <- list.files(path = "/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Data/swimming", recursive = TRUE,pattern = "\\.txt$", full.names = TRUE)

#Lapply allows to import all the files in one list
loop_full<-lapply(list_of_files, read.delim2)
names(loop_full)<-list_of_files
loop_full<-lapply(loop_full, function(x) { x["frame"] <- NULL; x })
```

```{r 12_loop}
mean_t1_12<-list()
# for loop to make same functions to all files of 12°C 
for (i in 1:14){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity
df$dist <- sqrt((df$XX)^2+(df$Y)^2) #Distance
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2]
z1$dist <- aggregate(df$dist, list(df$X), FUN = sum, na.rm=TRUE)[,2]
#Mean velocity by larvae
mean_t1_12[[i]]<-z1
}
names(mean_t1_12)<-list_of_files[1:14] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_12<-Map(cbind, mean_t1_12, group = names(mean_t1_12))
mean_t1_12<- list.rbind(mean_t1_12)
var <- basename(mean_t1_12$group)%>% tools::file_path_sans_ext()%>% strsplit(., "_")%>% do.call(rbind,.) %>% as.data.frame()
mean_t1_12 <- cbind(mean_t1_12,var)
mean_t1_12 <- mean_t1_12[,-5]

colnames(mean_t1_12)<-c("Trajectory","Time","IV","Dist","Temp","aquarium","Larva")
```

```{r 15_loop}
mean_t1_15<-list()
# for loop to make same functions to all files of 15°C 
for (i in 15:25){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity 
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2]
df$dist <- sqrt((df$XX)^2+(df$Y)^2) #Distance
z1$dist <- aggregate(df$dist, list(df$X), FUN = sum, na.rm=TRUE)[,2]
#Mean velocity by larvae
mean_t1_15[[i]]<-z1
}
mean_t1_15<-mean_t1_15[c(15:25)]
names(mean_t1_15)<-list_of_files[15:25] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_15<-Map(cbind, mean_t1_15, group = names(mean_t1_15))
mean_t1_15<- list.rbind(mean_t1_15)
var <- basename(mean_t1_15$group)%>% tools::file_path_sans_ext()%>% strsplit(., "_")%>% do.call(rbind,.) %>% as.data.frame()
mean_t1_15 <- cbind(mean_t1_15,var)
mean_t1_15 <- mean_t1_15[,-5]

colnames(mean_t1_15)<-c("Trajectory","Time","IV","Dist","Temp","aquarium","Larva")
```

```{r 17_loop}
mean_t1_17<-list()
# for loop to make same functions to all files of 17°C 
for (i in 26:39){ a=loop_full[[i]][,]
a$x<-as.numeric(a$x)
a$y<-as.numeric(a$y)
df<-a %>%
  group_by(X) %>%
  mutate(XX = x - lag(x)) %>% #Distance difference in x axis  between two points
  mutate(Y = y - lag(y)) #Distance difference in y axis between two points
df$time<-as.POSIXct(df$time, format="%M:%OS")
df$tdif<-ifelse(difftime(df$time,lag(df$time), units = "secs")<1,difftime(df$time,lag(df$time), units = "secs"),NA)
df$iv <- (sqrt((df$XX)^2+(df$Y)^2))/0.125 #Instant velocity 
z1<-aggregate(df$tdif, by=list(Trajectory=df$X), FUN=sum, na.rm=T)
z1$IV <- aggregate(df$iv, list(df$X), FUN = mean, na.rm=TRUE)[,2]
df$dist <- sqrt((df$XX)^2+(df$Y)^2) #Distance
z1$dist <- aggregate(df$dist, list(df$X), FUN = sum, na.rm=TRUE)[,2]
#Mean velocity by larvae
mean_t1_17[[i]]<-z1
}
mean_t1_17<-mean_t1_17[c(26:39)]
names(mean_t1_17)<-list_of_files[26:39] #rownames

# Tidying columns Temp, aquarium and larva with rownames
mean_t1_17<-Map(cbind, mean_t1_17, group = names(mean_t1_17))
mean_t1_17<- list.rbind(mean_t1_17) 
var <- basename(mean_t1_17$group)%>% tools::file_path_sans_ext()%>% strsplit(., "_")%>% do.call(rbind,.) %>% as.data.frame()
mean_t1_17 <- cbind(mean_t1_17,var)
mean_t1_17 <- mean_t1_17[,-5]

colnames(mean_t1_17)<-c("Trajectory","Time","IV","Dist","Temp","aquarium","Larva")

data<-rbind(mean_t1_12,mean_t1_15,mean_t1_17)
```

```{r swimm_tidy}
#Tidying data
data1<-data%>%group_by(Temp,aquarium,Larva) %>%
  dplyr::summarise(Ist_Vel = mean(IV),
                   Avg_time= mean(Time),
                   Tot_dist= sum(Dist),
                   Tot_Time= sum(Time),
                   Max_Time=max(Time))%>%rowid_to_column(var='ID')
data1$Temp<-as.factor(data1$Temp)
```

```{r Median_swimm}
#Median of instant velocity by temp
medIV <- ddply(data1, "Temp", summarise, grp.med=median(Ist_Vel), Q1=quantile(Ist_Vel, c(0.25), type = 6),Q3=quantile(Ist_Vel, c(0.75), type = 6), IQR=Q3-Q1)
print(medIV)
#Median of max time swimming by temp
medMax <- ddply(data1, "Temp", summarise, grp.med=median(Max_Time),
Q1=quantile(Max_Time, c(0.25), type = 6),Q3=quantile(Max_Time, c(0.75), type = 6), IQR=Q3-Q1)
print(medMax)
#Median of Total distance swimming by temp
medtotdist <- ddply(data1, "Temp", summarise, grp.med=median(Tot_dist),
Q1=quantile(Tot_dist, c(0.25), type = 6),Q3=quantile(Tot_dist, c(0.75), type = 6), IQR=Q3-Q1)
print(medtotdist)
#Median of Total time swimming by temp
medtottime <- ddply(data1, "Temp", summarise, grp.med=median(Tot_Time),
Q1=quantile(Tot_Time, c(0.25), type = 6),Q3=quantile(Tot_Time, c(0.75), type = 6), IQR=Q3-Q1)
print(medtottime)
```

## 2. Kernel plots

```{r Kernel_IV}
#Non-parametric Kernel Densities plot for instant velocity (IV)
dplot_IV<-ggplot(data1, aes(Ist_Vel, color=Temp))+
  geom_density(kernel = "gaussian")+
  theme_classic()+ 
  labs(colour="Temperature (°C)", x="Apparent Instant Velocity (mm/s)", y="Kernel density")+ 
  scale_x_continuous(limits = c(0, NA),breaks = 0:10, expand = expansion(mult = c(0, 0.1))) +
  scale_y_continuous(limits = c(0, NA),breaks =seq(from=0,to=1, by=0.1),
expand = expansion(mult = c(0, 0.1))) +
  theme(text = element_text(size = 10)) +
  scale_colour_manual(values=cbPalette)
dplot_IV <- dplot_IV + geom_vline(xintercept = 1.76, color="#008B45FF", linetype=2) + geom_vline(xintercept = 1.56, color="#EE0000FF", linetype=2) + geom_label(aes(x=1.56,y=0.42),color="#EE0000FF",size=3, label="17°C") + geom_vline(xintercept = 5.13,color="#3B4992FF", linetype=2) + geom_label(aes(x=5.13,y=0.14),color="#3B4992FF",size=3, label="12°C") + geom_label(aes(x=1.76,y=0.55),color="#008B45FF",size=3, label="15°C")
```

*Kernel density plot of instant velocity (IV) with their median*

```{r Kernel_MT}
#Non-parametric Kernel Densities plot for max time swimming (MT)
dplot_Max<-ggplot(data1, aes(Max_Time, color=Temp))+
  geom_density(kernel="gaussian")+
  theme_classic()+
  labs(colour="Temperature (°C)", x="Maximum Swimming Time (sec)", y="Kernel density")+ 
  scale_x_continuous(limits = c(0, NA),breaks = seq(from=0,to=50,by=5),expand = expansion(mult = c(0, 0.1))) +
  scale_y_continuous(limits = c(0, NA),breaks = seq(from=0,to=0.06,by=0.01),expand = expansion(mult = c(0, 0.1))) +
  theme(text = element_text(size = 10)) +
  scale_colour_manual(values = cbPalette)
dplot_Max<-dplot_Max + geom_vline(xintercept = 18.80, color="#008B45FF", linetype=2) + geom_vline(xintercept = 19.25, color="#EE0000FF", linetype=2) + geom_label(aes(x=19.25,y=0.034),color="#EE0000FF",size=3, label="17°C") + geom_vline(xintercept = 10.25,color="#3B4992FF", linetype=2) + geom_label(aes(x=10.25,y=0.057),color="#3B4992FF",size=3, label="12°C") + geom_label(aes(x=18.80,y=0.029),color="#008B45FF",size=3, label="15°C")
```

*Kernel density plot of max time swimming (MT) with their median*

```{r Kernel_totaldist}
#Non-parametric Kernel Densities plot for total distance (TD)

dplot_totaldist<-ggplot(data1, aes(Tot_dist, color=Temp))+
  geom_density(kernel="gaussian")+
  theme_classic()+ 
  scale_color_manual(values=cbPalette)+ 
  labs(color="Temperature (°C)", x="Total Swimming Distance (mm)", y="Kernel density") +
  theme(text = element_text(size = 10))

dplot_totaldist <- dplot_totaldist + geom_vline(xintercept = 171.2304, color="#008B45FF", linetype=2) + geom_vline(xintercept = 105.28, color="#EE0000FF", linetype=2) + geom_vline(xintercept = 112.35,color="#3B4992FF", linetype=2) + geom_label(aes(x=112.35,y=0.0036),color="#3B4992FF",size=3, label="12°C") + geom_label(aes(x=171.2304,y=0.0023),color="#008B45FF",size=3, label="15°C") + geom_label(aes(x=105.28,y=0.0058),color="#EE0000FF",size=3, label="17°C")
```

*Kernel density plot of total distance swimming (TD) with their median*


```{r Kernel_totaltime}
#Non-parametric Kernel Densities plot for total Time (TT)

dplot_totaltime<-ggplot(data1, aes(Tot_Time, color=Temp))+
  geom_density(kernel="gaussian")+
  theme_classic()+ 
  scale_color_manual(values=cbPalette)+ 
  labs(color="Temperature (°C)", x="Total Swimming Time (sec)", y="Kernel density") +
  theme(text = element_text(size = 10))

dplot_totaltime <- dplot_totaltime + geom_vline(xintercept = 51.20, color="#008B45FF", linetype=2) + geom_vline(xintercept = 54.35, color="#EE0000FF", linetype=2) + geom_vline(xintercept = 20.30,color="#3B4992FF", linetype=2) + geom_label(aes(x=20.30,y=0.0215),color="#3B4992FF",size=3, label="12°C") + geom_label(aes(x=51.20,y=0.0071),color="#008B45FF",size=3, label="15°C") + geom_label(aes(x=54.35,y=0.0157),color="#EE0000FF",size=3, label="17°C")
```

*Kernel density plot of total distance swimming (TD) with their median*


## 3. Linear mixed effects model with log transformed data

```{r lm_assmptn}
#Checking for normality
shapiro.test(log(data1$Ist_Vel))
hist(log(data1$Ist_Vel))
shapiro.test(log(data1$Max_Time))
hist(log(data1$Max_Time))
shapiro.test(log(data1$Tot_dist))
hist(log(data1$Tot_dist))
shapiro.test(log(data1$Tot_Time))
hist(log(data1$Tot_Time))

#Checking for heteroscedasticity
leveneTest(log(data1$Ist_Vel), data1$Temp)
leveneTest(log(data1$Max_Time),data1$Temp)
leveneTest(log(data1$Tot_dist), data1$Temp)
leveneTest(log(data1$Tot_Time),data1$Temp)
```

```{r swimm_lm}
#Linear mixed effects model with Log transformed data of IV. aquarium is a factor with random effects and larva is nested in aquarium 
modIV<-lmer(log(Ist_Vel)~Temp + (aquarium|Larva), data=data1)
summary(modIV)
anova(modIV)
#model diagnostic
plot(modIV,which = 1)
qqnorm(resid(modIV))
qqline(resid(modIV))


#Linear mixed effects model with Log transformed data of MT aquarium is a factor with random effects and larva is nested in aquarium 
modMax<-lmer(log(Max_Time)~Temp + (aquarium|Larva), data=data1)
summary(modMax)
anova(modMax)
#model diagnostic
plot(modMax,which = 1)
qqnorm(resid(modMax))
qqline(resid(modMax))


#Linear mixed effects model with Log transformed data of TD aquarium is a factor with random effects and larva is nested in aquarium 
moddist<-lmer(log(Tot_dist)~Temp + (aquarium|Larva), data=data1)
summary(moddist)
anova(moddist)
#model diagnostic
plot(moddist,which = 1)
qqnorm(resid(moddist))
qqline(resid(moddist))


#Linear mixed effects model with Log transformed data of TT aquarium is a factor with random effects and larva is nested in aquarium 
modtime<-lmer(log(Tot_Time)~Temp + (aquarium|Larva), data=data1)
summary(modtime)
anova(modtime)
#model diagnostic
plot(modtime,which = 1)
qqnorm(resid(modtime))
qqline(resid(modtime))

```

## 4. Pairwise comparisions and log transformed data plots

```{r swimm_pw}
#pairwise comparison using estimated means of instant velocity by temp
meansIV<-emmeans(modIV, pairwise ~ Temp, adjust="bonferroni")
meansIV

#pairwise comparison using estimated means of max time swimming by temp
meansMax<-emmeans(modMax, pairwise ~ Temp, adjust="bonferroni")
meansMax

#pairwise comparison using estimated means of total time swimming by temp
meanstime<-emmeans(modtime, pairwise ~ Temp, adjust="bonferroni")
meanstime

#pairwise comparison using estimated means of max time swimming by temp
meansdist<-emmeans(moddist, pairwise ~ Temp, adjust="bonferroni")
meansdist
```

## 5. Plots

```{r logIV_plot}
#Boxplot of logaritmic IV data 
p1<-ggplot(data1, aes(x=Temp, y=log(Ist_Vel), fill=Temp))+geom_boxplot(outliers = F)+
  stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") +
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic()+labs(x="Temperature (°C)", y="AIV")+theme(legend.position="none",text= element_text(size=10))+
   scale_fill_manual(values = cbPalette)+ 
  scale_y_continuous(breaks =c(1,2,0))+  geom_text(x=1.2,y=2.4,label="a",color="red", size = 3)+
  geom_text(x=2.2,y=1.4,label="b",color="red", size = 3)+
  geom_text(x=3.2,y=1.4,label="b",color="red", size = 3)
p1
```

*Boxplot that represents logarithmic AIV distribution of the data by
temperature, letters indicate significant difference.*

```{r logMT_plot}
# Boxplot of logaritmic MT data 
p2<-ggplot(data1, aes(x=Temp, y=log(Max_Time), fill=Temp))+
  geom_boxplot()+ stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") + 
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic() + theme(legend.position="none",text= element_text(size=10)) +
  labs(x="Temperature (°C)", y="MST")+
   scale_fill_manual(values=cbPalette)+
  geom_text(x=1.2,y=3.2,label="a",color="red",size = 3)+
  geom_text(x=2.2,y=3.7,label="a",color="red",size = 3)+
  geom_text(x=3.2,y=3.7,label="a",color="red",size = 3)+ scale_y_continuous(breaks = 0:4)
p2

```

*Boxplot that represents logarithmic MTS distribution of the data by
temperature, letters indicate significant difference.*

```{r logdits_plot}
# Boxplot of logaritmic dist data 
p3<-ggplot(data1, aes(x=Temp, y=log(Tot_dist), fill=Temp))+
  geom_boxplot(outliers = F)+ stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") + 
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic() + theme(legend.position="none",text= element_text(size=10)) +
  labs(x="Temperature (°C)", y="TSD")+
   scale_fill_manual(values=cbPalette)+
  geom_text(x=1.2,y=6.8,label="a",color="red",size = 3)+
  geom_text(x=2.2,y=6.8,label="a",color="red",size = 3)+
  geom_text(x=3.2,y=6.8,label="a",color="red",size = 3)
p3
```

*Boxplot that represents logarithmic TD distribution of the data by
temperature, letters indicate significant difference.*

```{r logtime_plot}
# Boxplot of logaritmic dist data 
p4<-ggplot(data1, aes(x=Temp, y=log(Tot_Time), fill=Temp))+
  geom_boxplot(outliers = F)+ stat_summary(fun.y =mean,geom="point",width=0.75,
  size=1,linetype="black") + 
  geom_jitter(color="black", size=0.6, alpha=0.3)+
  theme_classic() + theme(legend.position="none",text= element_text(size=10)) +
  labs(x="Temperature (°C)", y="TST")+
   scale_fill_manual(values=cbPalette)+
  geom_text(x=1.2,y=5,label="a",color="red",size = 3)+
  geom_text(x=2.2,y=5,label="ab",color="red",size = 3)+
  geom_text(x=3.2,y=5,label="b",color="red",size = 3)+ ylim(1,5)
p4
```

*Boxplot that represents logarithmic TT distribution of the data by
temperature, letters indicate significant difference.*

```{r Fig_4}
#kernel density plot with inset boxplot of IV
plot.with.inset.IV <-
  ggdraw() +
  draw_plot(dplot_IV) +
  draw_plot(p1, x = .45, y = 0.65, width = .3, height = .35)
plot.with.inset.IV
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/swimming/IV.pdf",dpi = 600)

```

*Fig 4. Kernel density plot of apparent instant velocity swimming by
larvae (AIV) with their median (triangle) by temperature, also with an
inside boxplot that represents the logarithmic AIV by temperature.*

```{r Fig_5}
#kernel density plot with inset boxplot of MT
plot.with.inset.Max_Time <-
  ggdraw() +
  draw_plot(dplot_Max) +
  draw_plot(p2, x = .45, y = 0.65, width = .3, height = .35)
plot.with.inset.Max_Time
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/swimming/max.pdf",dpi = 600)


```

*Fig 5. Kernel density plot of max time swimming by larvae (MTS) with
their median (triangle) by temperature, also with an inside boxplot that
represents the logarithmic MTS by temperature.*


```{r Fig_6}
#kernel density plot with inset boxplot of TT
plot.with.inset.Totaltime <-
  ggdraw() +
  draw_plot(dplot_totaltime) +
  draw_plot(p4, x = .45, y = 0.65, width = .3, height = .35)
plot.with.inset.Totaltime
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/swimming/Total.pdf",dpi = 600)
```


```{r Fig_7}
#kernel density plot with inset boxplot of TT
plot.with.inset.Totaldist<-
  ggdraw() +
  draw_plot(dplot_totaldist) +
  draw_plot(p3, x = .45, y = 0.65, width = .3, height = .35)
plot.with.inset.Totaldist
#ggsave("/Users/lucasb/Library/CloudStorage/GoogleDrive-lucasbravog98@gmail.com/Unidades compartidas/Bravo-Guzman et al/Austral ecology/Resultados/swimming/Totaldist.pdf",dpi = 600)
```